---
title: "Time Series Toolkit Package"
author: "Coleman Zhang"
date: "October 8, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a document on Time Series Toolkit Package. There are three tools in this package: tscor, tsplot, and tscorplot.

First, let's generate a random 10-by-10 matrix as an example. This matrix will be our time series matrix, with rows as different time series, and columns as time periods.

```{r 1}
mat <- matrix(rnorm(200), ncol=20)
mat
```

## 1. tscor: returns a correlation matrix of an n-by-t time series matrix

We have n time series in our matrix. To compute correlation matrix, we take pairwise correlation of n rows. The function will return an n-by-n matrix

```{r 2,warning=FALSE}
library(tstool)
library(reshape2)
library(ggplot2)
```

```{r 4,results='hide', message=FALSE, warning=FALSE}
tscor(mat)
```
## 2. tsplot: returns a plot of n time series
```{r 5}
tsplot(mat)
```


## 3. tscorplot: generate a correlation matrix heat map

```{r 3}
tscorplot(mat)
```
